Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2023-07-03 popl24/intro.tex
checkpoint

>>>>

In summary, our analysis takes a ``just do it'' approach- rather than
using, e.g., traditional security type or linear type disciplines to
prevent ``bad things'' from happening, we base our analysis on precise
quantification of intensional protocol behavior and especially
dependencies between secret inputs, public outputs, and adversarial
views of protocols. We ameliorate scalability issues associated with
fine-grained analysis by manually establishing compositional
properties inspired by probabilistic separation logic
\cite{barthe2019probabilistic}, obtaining a middle-ground, scalable
``proof assistant'' style approach enabled by MPC protocol paradigms.
